Applying the optimized ensemble histogram method to the square-well liquid

### 2014-07-06 papers/square-well-liquid/histogram-paper.tex
define "flat" as multiple gaussian adjustments Tested on darcy. Took 0:35.94.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-rdf}
  \caption{Radial distribution function.\label{fig:rdf}}
\end{figure}

@@

>>>>

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-rdf}
%%   \caption{Radial distribution function.\label{fig:rdf}}
%% \end{figure}

@@

\textcolor{red}{I think maybe we only want to keep ``pushing down the
  bubbles'' so long as the variance increases.  I'm afraid that if the
  variance drops we could possibly create a dangerous hole when we try
  pushing down a sharp and pointy bubble...}
